Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-01-14 grove-paper.tex
add sorts to arity function results
Added notes and links to CRDT related work

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P)                                        \\
      \hline
      \arity(\Root)={}        & \left\{ \Root \right\}                         \\
      \arity(\PatVar)={}      & \left\{ \right\}                               \\
      \arity(\ExpVar)={}      & \left\{ \right\}                               \\
      \arity(\ExpLam)={}      & \left\{ \mathtt{Param}, \mathtt{Type}, \mathtt{Body} \right\} \\
      \arity(\ExpApp)={}      & \left\{ \mathtt{Fun}, \mathtt{Arg} \right\}              \\
      \arity(\ExpPlus)={}     & \left\{ \mathtt{L}, \mathtt{R} \right\}         \\
      \arity(\ExpTimes)={}    & \left\{ \mathtt{L}, \mathtt{R} \right\}         \\
      \arity(\ExpNum)={}      & \left\{ \right\}                               \\
      \arity(\TypArrow)={}    & \left\{ \mathtt{Arg}, \mathtt{Result} \right\}       \\
      \arity(\TypNum)={}      & \left\{ \right\}                               \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

@@

The Causal Graph CRDT for Complex Document Structure

\url{https://en.wikipedia.org/wiki/Conflict-free_replicated_data_type}
 - LWW-Element-Set (Last-Write-Wins-Element-Set)
 - OR-Set (Observed-Remove Set)

G-Set
2P-Set
PN-Set
LWW-element-Register
OR-Set
MV-Register: Multi-Value Register
U-Set (this is what we are for edges, not OR-set due to duplicates)
Add-Remove Partial Order data type
  2P-Set for vertices, and a G-Set for edges.

@@

https://crdt.tech/papers.html
[35]
    Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]

        Keywords: trees

[41]
    Martin Kleppmann and Alastair R Beresford. A conflict-free replicated JSON datatype. IEEE Transactions on Parallel and Distributed Systems, 28(10):2733--2746, April 2017. [ bib | DOI | arXiv ]

        Keywords: trees

[67]
    Vinh Tao, Marc Shapiro, and Vianney Rancurel. Merging semantics for conflict updates in geo-distributed file systems. In 8th ACM International Systems and Storage Conference, SYSTOR 2015. ACM, May 2015. [ bib | DOI | .pdf ]

        Keywords: trees

[95]
    Mehdi Ahmed-Nacer, Stéphane Martin, and Pascal Urso. File system on CRDT. Research Report RR-8027, INRIA, July 2012. [ bib | arXiv | http ]

        Keywords: trees

[103]
    Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]

        Keywords: trees, undo

>>>>

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P \times \{Exp, Pat, Typ\}) \\
      \hline
      \arity(\Root)={} & \left\{ \Root \right\} \\
      \arity(\PatVar)={} & \left\{ \right\} \\
      \arity(\ExpVar)={} & \left\{ \right\} \\
      \arity(\ExpLam)={} & \left\{ (\mathtt{Param}, Pat), (\mathtt{Type}, Typ), (\mathtt{Body}, Exp) \right\} \\
      \arity(\ExpApp)={} & \left\{ (\mathtt{Fun}, Exp), (\mathtt{Arg}, Exp) \right\} \\
      \arity(\ExpPlus)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpTimes)={} & \left\{ (\mathtt{L}, Exp), (\mathtt{R}, Exp) \right\} \\
      \arity(\ExpNum)={} & \left\{ \right\} \\
      \arity(\TypArrow)={} & \left\{ (\mathtt{Arg} Typ), (\mathtt{Result}, Typ) \right\} \\
      \arity(\TypNum)={} & \left\{ \right\} \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

A commutative replicated data type for cooperative editing
  \url{https://hal.inria.fr/inria-00445975/document}
  Describes TreeDoc but this uses a document model that is a list (tree is just how it is implemented)

Logoot : a Scalable Optimistic Replication Algorithm for Collaborative Editing on P2P Networks
  \url{}

Specification and Complexity of Collaborative Text Editing
  \url{https://www.microsoft.com/en-us/research/wp-content/uploads/2016/07/podc16-complete.pdf}

@@

The Causal Graph CRDT for Complex Document Structure
  \url{https://dl.acm.org/doi/10.1145/3209280.3229110}

\url{https://en.wikipedia.org/wiki/Conflict-free_replicated_data_type}

G-Set
PN-Set
2P-Set
LWW-element-Set (Last-Write-Wins)
OR-Set
MV-Register: Multi-Value Register
U-Set (this is what we are for edges, not OR-set due to duplicates)
Add-Remove Partial Order data type
  2P-Set for vertices, and a G-Set for edges.

@@

https://crdt.tech/papers.html

Mahsa Najafzadeh, Marc Shapiro, and Patrick Eugster. Co-design and verification of an available file system. In 19th International Conference on Verification, Model Checking, and Abstract Interpretation, VMCAI 2018, pages 358--381. Springer LNCS volume 10747, January 2018. [ bib | DOI | .pdf ]
  http://dx.doi.org/10.1007/978-3-319-73721-8_17
  https://pages.lip6.fr/Marc.Shapiro/papers/VMCAI-2018-filesys.pdf

Martin Kleppmann and Alastair R Beresford. A conflict-free replicated JSON datatype. IEEE Transactions on Parallel and Distributed Systems, 28(10):2733--2746, April 2017. [ bib | DOI | arXiv ]
  http://dx.doi.org/10.1109/TPDS.2017.2697382
  http://arxiv.org/abs/1608.03960

Vinh Tao, Marc Shapiro, and Vianney Rancurel. Merging semantics for conflict updates in geo-distributed file systems. In 8th ACM International Systems and Storage Conference, SYSTOR 2015. ACM, May 2015. [ bib | DOI | .pdf ]
  http://dx.doi.org/10.1145/2757667.2757683
  https://pages.lip6.fr/Marc.Shapiro/papers/geodistr-FS-Systor-2015.pdf

Mehdi Ahmed-Nacer, Stéphane Martin, and Pascal Urso. File system on CRDT. Research Report RR-8027, INRIA, July 2012. [ bib | arXiv | http ]
  http://arxiv.org/abs/1207.5990
  https://hal.inria.fr/hal-00720681/

Stéphane Martin, Pascal Urso, and Stéphane Weiss. Scalable XML collaborative editing with undo. In On the Move to Meaningful Internet Systems (OTM), pages 507--514. Springer LNCS volume 6426, October 2010. [ bib | DOI | arXiv ]
  http://dx.doi.org/10.1007/978-3-642-16934-2_37
  http://arxiv.org/abs/1010.3615
